MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
completed graph for win/loss
new code- hand theory

>>>>

```{r}
#Summary of total points
ptssum<- cast(df1, GAME_ID1+ player_id + player_name  ~ PTS); head(ptssum)
#creating "total points per player, per game" column
ptssum$totalpts<- ptssum[,"2"]*2 + ptssum[,"3"]*3

pttsum2<-ptssum[order(ptssum$totalpts,decreasing=TRUE),]
head(pttsum2,10)
```

```{r}
###Hot Hand Theory

#Set the value to character
df[, "SHOT_RESULT"] <- as.character(df[, "SHOT_RESULT"])

#Define 1 for baskets made and 0 for baskets missed. We need a vector to use it to our function below.
shotresult <- c()
for(i in 1:nrow(df)) {
  if(shots[i] == 'missed') shotresult <- c(shotresult, 0)
  else if(shots[i] == 'made') shotresult <- c(shotresult, 1)
}

shotresult

#Set the value to numeric/integer
df[, "SHOT_RESULT"] <- as.numeric(df[, "SHOT_RESULT"])
df[ ,'SHOT_NUMBER'] <- as.integer(df[ , 'SHOT_NUMBER'])

#Define the length of a shooting streak to be the number of consecutive baskets made until a miss occurs
#Create a function that gives us a vector with the number of streaks
number_of_streaks <- function(x) {
  x <- c(0, x, 0)
  which_zero <- which(x == 0)
  streak <- diff(which_zero) - 1
  streak
}

number_of_streaks(shotresult)

player_and_game <- function(x, y) {
   player <- df[df[ ,'player_id'] == x & df[ ,'GAME_ID1'] == y, 'FGM']
   number_of_streaks(as.vector(player))
}
player_and_game(202681, 21400681)

ourtable <- head(pttsum2,10)

list_per_player <- list()
j <- 1
for(i in ourtable$player_id) {
   streak_per_player[[j]] <- player_and_game(i, ourtable[ourtable[ ,'player_id'] == i, 'GAME_ID1'])
   j <- j + 1
}
streak_per_player
